\chapter{Implementation}

The implementation of the application required the use of three different programming languages each with their own specific task. In order to create a GUI we were forced to use JavaScript as this is the only option Samsung has made available for creating apps. However, the peer-to-peer engine, libswift, is written in C++ which meant that no matter what, we would also have to run C++ code in harmony with JavaScript. As we would be running C++ anyway and due to the complexity of the core of the application we decided to build the core, which manages downloads, uploads and streams, in C++ as well. This made managing the libswift library easier than it would have been from JavaScript. Documentation for the C++ code can be found in the \hyperref[sec:Doxygen]{appendix}

A language wrapper between C++ and JavaScript was not found, and could not have been used anyway because of the sandboxed environment. A solution we found to connect the JavaScript front-end with the C++ back-end was to use HTTP GET requests. By running an HTTP web server written in C++, a client-server communication mechanism could be built between the two languages. The JavaScript client can send HTTP requests to the server, and the server can perform the necessary function calls to the libswift engine and the other code necessary for the project. A small drawback is that the current firmware version of the tv does not have HTML5, which has support for websockets. Websockets remove the need of continuous polling, and allow the server to send responses(results) back whenever he's ready, without blocking the client. 

In order to implement search functionality we made use of dispersy(message handling system used in Tribler) and a DHT (distributed hash table), both of which are written in python. In order to initialise both services and execute searches we needed a small amount of Python to manage dispersy and DHT. For this purpose a language wrapper was sufficient.The link between C++ and Python was provided by the Python/C API\footnote{\url{http://docs.python.org/c-api/}}.

\section{JavaScript}
The JavaScript front-end consists of 5 scenes (classes), namely Main, Browse, Downloads, Player and Settings.
These scenes are the five graphical elements the front-end is able to switch to and from.
In the Browse scene, functionality is built to: search remotely, browse usb devices, download or stream files,
upload files and add files to a playlist. In the Downloads scene, the progress of downloads and uploads is visualized.
In the Player scene, videos in the playlist can be played, and the streams can be watched.
In the Settings scene some settings can be set, like the download path and limitations to upload and download speed.
Most of this functionality is actually done by the C++ code, but in the scenes HTTP GET requests are sent to the webserver to execute the functions.

\section{C++}
The implementation of the C++ part ended up being quite different from the business class diagram, which can be found in the requirements chapter. The main reason for this is that the functionality of the filemanager could be done in JavaScript and as a result the necessity for that functionality in C++ dissapeared. There was also no need for a seperate download and upload class because in libswift a download and an upload are essentially the same thing. When you are downloading you are also automatically uploading and an upload is just a download at 100\% completion. These changes meant that the end product looks a lot like the the class diagram in the design chapter.

\section{Python}
Implementing the Python part was as easy as it should be, since everything was already available from Tribler. The only thing needed to do was to call the methods we need and disable all other parts we do not use. 
Some patches were required in Tribler code, but were very easy to apply. The only file we made in Python was the DispersyInterface, which actually starts a Tribler session with only DHT and dispersy. 
To save resources, we were recommended to disable all the other parts of Tribler, since they are not used in our software.

\section{Changes during development}
During development it is almost inevitable that there will be changes from the original design. In this part we will discuss the largest changes we decided to make or were forced to make.

\subsection{Software Improvement Group}
Our code was evaluated by the Software Improvement Group\footnote{\url{http://www.sig.eu/nl/}}, which checks the overall quality of software projects such as ours. 
During this project, we sent them our code twice. In general, they were satisfied with the quality of our code and documentation, meaning that our
code is maintained well. Our only flaw was that certain methods were implemented in too many lines, making them complex.
The solution to this was to break these methods up in submethods, which are then called in the original method. Also, we were not aware that the testsuite 
had to be sent as well, so they were not able to check our testsuite. At the time we sent our code for the first time to SIG, however, we already had a test suite testing
the crucial parts of our system.

The second feedback confirmed our efforts in improving the code according to the guidelines the group gave us the first time.
Even though our code scored better at some parts, it also scored less on other parts. Compared to the code we gave the first time,
the code for the second feedback contained a lot of code which depend on each other. In other words, the coupling was a bit tighter than before.
One of the reasons for this is that we extracted duplicate code from different files and implemented them in Settings.cpp, making Settings.cpp
a generic file containing helper-functions. The result was that most files depend on Settings.cpp, because it contains a lot of generic functions.
Even though our code grew a lot, we still managed to maintain the code well in general.

Their feedback can be found in the \hyperref[sec:sig]{appendix}.

\subsection{Upload visibility}

There were a number of options when it came to choosing how to decide which files would be uploaded. In the design we chose for a setting per file which could be set to true or false by the user which determined whether the file would be shared with others. Due to limited time and the fact that FileManager was no longer going to be implemented in C++ we decided to change the way users determine what should be uploaded.
\\\\
All files in the default dowload folder automatically start uploading on startup. The user can browse to files on the tv and choose to upload them. Any files in the list of uploads and downloads can also be stopped and removed by the user to stop them from uploading. This implementation saved us some time by using functionality that was already implemented rather than needing to add another setting and having to remember whether a file has been set to visible or not.

\subsection{Number of downloads}

In the original design the plan was to allow the user to be able to download multiple files at the same time. This would be possible in principle and could easily be implemented in our application. However, in order to save processor power on the TV we decided to limit the user to one download at a time. The user is able to switch between downloads and the application automatically starts downloading the next download in the list after it has finished.

\subsection{Excluded features}

Due to limited time and hardware some features were not implemented at all so that we could focus more on the features we believed to be most important. One of these features was the ability to rename files which was a should have according to our design. However, we decided to drop this functionality as it is a very minor feature which would take a relatively large amount of time to implement. At the time there were more major features that needed to be implemented.
\\\\
Another feature that was not implemented was sorting files by name, date, size and type. Just like renaming files this feature was not worth spending a lot of time on as it would not be a significant improvement to the application. Both of these features would be more important for a finished product but because we were focussing on creating a proof of concept other features took priority.
